Adaptive broadcast tree for multicores

### 2013-05-17 paper.tex
Ooops

>>>>

%--------------------------------------------------
\subsubsection{Comparison to shared-memory implementations}

A shared memory equivalent implementation for atomic broadcasts could
be:
\begin{itemize}
\item Messages should (but don't have to be) cache-line size. This
  prevents false-sharing. Larger messages can be fragmented. 
\item A FIFO queue that guarantees the order of messages (and therefore
  a lock)
\item A counter that is incremented whenever a process reads the
  message from the FIFO queue. To guarantee atomic broadcast
  attributes, elements from the queue must not be removed before all
  processes have read it.
\end{itemize}

This sounds pretty expensive. Need to evaluate this. The question is
whether any sane person would use such a queue for high level
applications. If so, which ones?

There are some libraries providing synchronization primitives such as
barriers, critical sections, atomic updates and locks.

\begin{itemize}
\item Is there an OpenMP equivalent? \emph{OpenMP} has a shared-memory
  based programming model that is targeted to the HPC
  world. \stefan{So what exactly is the relationship between OpenMP
    and MPI? MPI seems to be more low-level. Does OpenMP implement
    MPI?}
\item \emph{Pthreads} also has a shared-memory model for low-end
  systems~\cite{OpenMP_paper}
\end{itemize}
